### 2011-11-07 doc/pldi2012/experiments.tex
removal of tree search benchmark, scaling of some figures/tables

To measure Legion's ability to distribute work across a distributed machine, 
three benchmarks were developed and run on a small cluster under a variety
of configurations.  The cluster consists of four nodes connected by a 40~Gb/s
Infiniband fabric.  Each node is powered by 2 Intel Xeon X5680 CPUs, each
with 6 cores, and 2 NVIDIA Tesla C2070 GPUs.  The cluster is running Linux
with GASNet using the {\tt ibv} conduit to interface directly with the standard
OFED software stack for low-latency access to the Infiniband hardware.

@@

\begin{figure}
  \centering
  \subfigure[Performance Scaling]{
    \begin{tikzpicture}
      \begin{axis}[xlabel=Number of Nodes,ylabel=Normalized Speedup,height=5cm,width=8.5cm,xtick={1,2,3,4}]
        \addplot coordinates {
% num gpus = 2
  (1, 1.99)
  (2, 3.46)
  (3, 3.44)
  (4, 5.90)
        };
        \addplot coordinates {
% num gpus = 1
  (1, 1.00)
  (2, 1.86)
  (3, 2.40)
  (4, 3.41)
        };
      \legend{2 GPU/node,1 GPU/node}
      \end{axis}
    \end{tikzpicture}
    \label{sfig:results1:perf}
  }

  \subtable[Execution Time Breakdown]{
   \tiny
    \begin{tabular}{c@{\hspace{2pt}}cD{.}{.}{3}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}}
\toprule
GPUs/ & \# \\
node & nodes & \multicolumn{1}{c}{Wall Clock} & \multicolumn{1}{c}{Application} & \multicolumn{1}{c}{Copies} & \multicolumn{1}{c}{High-level} & \multicolumn{1}{c}{Low-level} & \multicolumn{1}{c}{Mapper} & \multicolumn{1}{c}{System} \\
\midrule
\multirow{4}{*}{$1$} & $1$ & 106.892 & 105.387 & 1.578 & 0.003 & 21.624 & 0 & 0\\
 & $2$ & 57.388 & 105.407 & 10.348 & 0.003 & 15.177 & 0 & 0.001\\
 & $3$ & 44.552 & 105.41 & 11.935 & 0.003 & 11.695 & 0 & 0.002\\
 & $4$ & 31.368 & 105.42 & 12.875 & 0.004 & 8.419 & 0 & 0.003\\
\midrule
\multirow{4}{*}{$2$} & $1$ & 53.787 & 105.397 & 1.857 & 0.004 & 10.953 & 0 & 0\\
 & $2$ & 30.923 & 105.415 & 10.716 & 0.004 & 7.937 & 0 & 0.002\\
 & $3$ & 31.037 & 105.414 & 12.558 & 0.004 & 7.996 & 0 & 0.001\\
 & $4$ & 18.103 & 105.42 & 13.747 & 0.004 & 4.638 & 0 & 0.003\\
\bottomrule \\
    \end{tabular}
    \label{sfig:results1:timers}
  }
  \caption{Circuit Simulator Results}
\end{figure}

@@

\begin{figure}
  \centering
  \subfigure[Performance Scaling]{
    \begin{tikzpicture}
      \begin{axis}[xlabel=Number of Nodes,ylabel=Normalized Speedup,height=5cm,width=8.5cm,xtick={1,2,3,4}]
        \addplot coordinates {
% 12 CPUs
  (1, 5.29)
  (2, 7.34)
  (3, 7.30)
  (4, 10.14)
        };
        \addplot coordinates {
% 6 CPUs
  (1, 4.51)
  (2, 6.00)
  (3, 6.57)
  (4, 8.83)
        };
        \addplot coordinates {
% 4 CPUs
  (1, 3.36)
  (2, 4.05)
  (3, 5.86)
  (4, 6.68)
        };
        \addplot coordinates {
% 3 CPUs
  (1, 2.58)
  (2, 3.55)
  (3, 4.35)
  (4, 5.61)
        };
        \addplot coordinates {
% 2 CPUs
  (1, 1.83)
  (2, 2.43)
  (3, 3.48)
  (4, 4.15)
        };
        \addplot coordinates {
% 1 CPUs
  (1, 1.00)
  (2, 1.61)
  (3, 1.87)
  (4, 2.33)
        };
      \legend{12 CPU/node,6 CPU/node,4 CPU/node,3 CPU/node,2 CPU/node,1 CPU/node}
      \end{axis}
    \end{tikzpicture}
    \label{sfig:results2:perf}
  }

  \subtable[Execution Time Breakdown]{
   \tiny
    \begin{tabular}{c@{\hspace{2pt}}cD{.}{.}{3}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}}
\toprule
GPUs/ & \# \\
node & nodes & \multicolumn{1}{c}{Wall Clock} & \multicolumn{1}{c}{Application} & \multicolumn{1}{c}{Copies} & \multicolumn{1}{c}{High-level} & \multicolumn{1}{c}{Low-level} & \multicolumn{1}{c}{Mapper} & \multicolumn{1}{c}{System} \\
\midrule
\multirow{4}{*}{$1$} & $1$ & 40.718 & 38.486 & 0.008 & 0.996 & 0.544 & 0 & 0\\
 & $2$ & 25.365 & 43.602 & 0.455 & 2.027 & 0.682 & 0 & 0.043\\
 & $3$ & 21.808 & 49.256 & 0.513 & 2.377 & 0.765 & 0 & 0.06\\
 & $4$ & 17.476 & 53.181 & 0.501 & 2.912 & 0.743 & 0 & 0.072\\
\midrule
\multirow{4}{*}{$2$} & $1$ & 22.289 & 38.55 & 0.009 & 1.694 & 0.68 & 0 & 0\\
 & $2$ & 16.787 & 51.081 & 0.573 & 2.373 & 0.756 & 0 & 0.056\\
 & $3$ & 11.706 & 49.502 & 0.733 & 2.661 & 0.749 & 0 & 0.072\\
 & $4$ & 9.817 & 50.798 & 0.86 & 2.755 & 0.735 & 0 & 0.1\\
\midrule
\multirow{4}{*}{$3$} & $1$ & 15.799 & 38.507 & 0.01 & 2.056 & 0.765 & 0 & 0\\
 & $2$ & 11.462 & 48.698 & 0.951 & 2.682 & 0.819 & 0 & 0.109\\
 & $3$ & 9.363 & 50.786 & 1.282 & 2.976 & 0.767 & 0 & 0.081\\
 & $4$ & 7.26 & 51.778 & 1.285 & 3.172 & 0.818 & 0 & 0.117\\
\midrule
\multirow{4}{*}{$4$} & $1$ & 12.11 & 39.296 & 0.011 & 2.17 & 0.827 & 0 & 0\\
 & $2$ & 10.05 & 49.799 & 1.145 & 3.023 & 0.82 & 0 & 0.24\\
 & $3$ & 6.951 & 51.216 & 1.367 & 3.137 & 0.798 & 0 & 0.12\\
 & $4$ & 6.093 & 52.183 & 1.216 & 3.317 & 0.782 & 0 & 0.135\\
\midrule
\multirow{4}{*}{$6$} & $1$ & 9.031 & 40.265 & 0.013 & 2.536 & 0.969 & 0 & 0\\
 & $2$ & 6.79 & 48.992 & 0.946 & 3.182 & 0.937 & 0 & 0.145\\
 & $3$ & 6.199 & 51.904 & 1.061 & 3.752 & 0.909 & 0 & 0.185\\
 & $4$ & 4.612 & 52.603 & 1.238 & 3.712 & 0.872 & 0 & 0.222\\
\midrule
\multirow{4}{*}{$12$} & $1$ & 7.704 & 45.959 & 0.03 & 4.01 & 1.765 & 0 & 0\\
 & $2$ & 5.547 & 65.432 & 1.019 & 4.762 & 1.328 & 0 & 0.232\\
 & $3$ & 5.577 & 68.74 & 1.059 & 5.922 & 1.384 & 0 & 0.322\\
 & $4$ & 4.017 & 67.662 & 1.19 & 4.882 & 1.22 & 0 & 1.485\\
\bottomrule \\
    \end{tabular}
    \label{sfig:results2:timers}
  }

@@

\subsection{Tree Search}

The circuit simulation was able to count on a static, if irregular,
partition of its workload, but that is not possible in some cases.  One
such example arises in ray tracing, in which the components of a scene to be
rendered are partitioned in a binary tree to minimize the number of expensive
object intersection tests that must be performed.  By traversing its path 
through the tree, a ray is able to efficiently skip entire chunks of the 
scene that it is guaranteed not to intersect with.  The trees tend to be
highly imbalanced (often intentionally so), and the set of rays that traverse
the tree tend to have similar path.  Both of these factors contribute to
large fluctuations in the load on any particular part of the tree, complicating
attempts to statically partition the tree.  The {\tt Tree Search} benchmark
explores Legion's ability to load-balance tasks in a locality-aware manner.

The benchmark constructs an irregular binary tree, and then partitions it into
roughly subregions that have roughly equal numbers of nodes.  Partition
crossings are annotated on the tree and traversal tasks are re-spawned when
a ray crosses into another partition.  Load imbalances will occur, but when
they do, the default mapper's ability to provide a set of tasks with good
locality should minimize the amount of data that must be copied around.  To
measure this benefit, each run is also done with the tree partitioning 
disabled.  This denies the mapper the locality information it would need to 
make good choices, reducing it to making essentially random choices.

Figure~\ref{sfig:results3:perf} shows performance of the tree search test
relative to the single node with partitioning case. MORE TEXT HERE.

\begin{figure}
  \centering
  \subfigure[Performance Scaling]{
    \begin{tikzpicture}
      \begin{axis}[xlabel=Number of Nodes,ylabel=Normalized Speedup,height=5cm,width=8.5cm,xtick={1,2,3,4}]
        \addplot coordinates {
% num gpus = 2
  (1, 1.99)
  (2, 3.46)
  (3, 3.44)
  (4, 5.90)
        };
        \addplot coordinates {
% num gpus = 1
  (1, 1.00)
  (2, 1.86)
  (3, 2.40)
  (4, 3.41)
        };
      \legend{2 GPU/node,1 GPU/node}
      \end{axis}
    \end{tikzpicture}
    \label{sfig:results3:perf}
  }

  \subtable[Execution Time Breakdown]{
   \tiny
    \begin{tabular}{c@{\hspace{2pt}}cD{.}{.}{3}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}}
\toprule
GPUs/ & \# \\
node & nodes & \multicolumn{1}{c}{Wall Clock} & \multicolumn{1}{c}{Application} & \multicolumn{1}{c}{Copies} & \multicolumn{1}{c}{High-level} & \multicolumn{1}{c}{Low-level} & \multicolumn{1}{c}{Mapper} & \multicolumn{1}{c}{System} \\
\midrule
\multirow{4}{*}{$1$} & $1$ & 106.892 & 105.387 & 1.578 & 0.003 & 21.624 & 0 & 0\\
 & $2$ & 57.388 & 105.407 & 10.348 & 0.003 & 15.177 & 0 & 0.001\\
 & $3$ & 44.552 & 105.41 & 11.935 & 0.003 & 11.695 & 0 & 0.002\\
 & $4$ & 31.368 & 105.42 & 12.875 & 0.004 & 8.419 & 0 & 0.003\\
\midrule
\multirow{4}{*}{$2$} & $1$ & 53.787 & 105.397 & 1.857 & 0.004 & 10.953 & 0 & 0\\
 & $2$ & 30.923 & 105.415 & 10.716 & 0.004 & 7.937 & 0 & 0.002\\
 & $3$ & 31.037 & 105.414 & 12.558 & 0.004 & 7.996 & 0 & 0.001\\
 & $4$ & 18.103 & 105.42 & 13.747 & 0.004 & 4.638 & 0 & 0.003\\
\bottomrule \\
    \end{tabular}
    \label{sfig:results3:timers}
  }
  \caption{Tree Search Results}
\end{figure}

>>>>

To measure Legion's ability to distribute work across a distributed machine, 
two real-world benchmarks were developed and run on a small cluster under a
variety of configurations.  The cluster consists of four nodes connected by a
40~Gb/s Infiniband fabric.  Each node is powered by 2 Intel Xeon X5680 CPUs,
each with 6 cores, and 2 NVIDIA Tesla C2070 GPUs.  The cluster is running Linux
with GASNet using the {\tt ibv} conduit to interface directly with the standard
OFED software stack for low-latency access to the Infiniband hardware.

@@

\pgfplotsset{every axis legend/.append style={
  font=\tiny,
  at={(0.02,0.98)},
  anchor=north west},
  cycle list={{black, mark=x}, {black, mark=+},
              {black, mark=o}, {black, mark=diamond},
              {black, mark=triangle}, {black, mark=star}}}

\begin{figure}
  \centering
  \subfigure[Performance Scaling]{
    \begin{tikzpicture}[scale=0.8]
      \begin{axis}[xlabel=Number of Nodes,ylabel=Normalized Speedup,height=5cm,width=8.5cm,xtick={1,2,3,4},font=\small]
        \addplot coordinates {
% num gpus = 2
  (1, 1.99)
  (2, 3.46)
  (3, 3.44)
  (4, 5.90)
        };
        \addplot coordinates {
% num gpus = 1
  (1, 1.00)
  (2, 1.86)
  (3, 2.40)
  (4, 3.41)
        };
      \legend{2 GPU/node,1 GPU/node}
      \end{axis}
    \end{tikzpicture}
    \label{sfig:results1:perf}
  }

  \subtable[Execution Time Breakdown]{
    \scalebox{0.8}{
   \tiny
    \begin{tabular}{c@{\hspace{2pt}}cD{.}{.}{3}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}}
\toprule
GPUs/ & \# \\
node & nodes & \multicolumn{1}{c}{Wall Clock} & \multicolumn{1}{c}{Application} & \multicolumn{1}{c}{Copies} & \multicolumn{1}{c}{High-level} & \multicolumn{1}{c}{Low-level} & \multicolumn{1}{c}{Mapper} & \multicolumn{1}{c}{System} \\
\midrule
\multirow{4}{*}{$1$} & $1$ & 106.892 & 105.387 & 1.578 & 0.003 & 21.624 & 0 & 0\\
 & $2$ & 57.388 & 105.407 & 10.348 & 0.003 & 15.177 & 0 & 0.001\\
 & $3$ & 44.552 & 105.41 & 11.935 & 0.003 & 11.695 & 0 & 0.002\\
 & $4$ & 31.368 & 105.42 & 12.875 & 0.004 & 8.419 & 0 & 0.003\\
\midrule
\multirow{4}{*}{$2$} & $1$ & 53.787 & 105.397 & 1.857 & 0.004 & 10.953 & 0 & 0\\
 & $2$ & 30.923 & 105.415 & 10.716 & 0.004 & 7.937 & 0 & 0.002\\
 & $3$ & 31.037 & 105.414 & 12.558 & 0.004 & 7.996 & 0 & 0.001\\
 & $4$ & 18.103 & 105.42 & 13.747 & 0.004 & 4.638 & 0 & 0.003\\
\bottomrule \\
    \end{tabular}
}
    \label{sfig:results1:timers}
  }
  \caption{Circuit Simulator Results}
\end{figure}

@@

\usepgflibrary{plotmarks}
\begin{figure}
  \centering
  \subfigure[Performance Scaling]{
    \begin{tikzpicture}[scale=0.8]
      \begin{axis}[
          xlabel=Number of Nodes,
          ylabel=Normalized Speedup,
          height=5cm,
          width=8.5cm,
          xtick={1,2,3,4},
          legend columns=3,
          font=\small
        ]
        \addplot coordinates {
% 12 CPUs
  (1, 5.29)
  (2, 7.34)
  (3, 7.30)
  (4, 10.14)
        };
        \addplot coordinates {
% 6 CPUs
  (1, 4.51)
  (2, 6.00)
  (3, 6.57)
  (4, 8.83)
        };
        \addplot coordinates {
% 4 CPUs
  (1, 3.36)
  (2, 4.05)
  (3, 5.86)
  (4, 6.68)
        };
        \addplot coordinates {
% 3 CPUs
  (1, 2.58)
  (2, 3.55)
  (3, 4.35)
  (4, 5.61)
        };
        \addplot coordinates {
% 2 CPUs
  (1, 1.83)
  (2, 2.43)
  (3, 3.48)
  (4, 4.15)
        };
        \addplot coordinates {
% 1 CPUs
  (1, 1.00)
  (2, 1.61)
  (3, 1.87)
  (4, 2.33)
        };
      \legend{12 CPU/node,6 CPU/node,4 CPU/node,3 CPU/node,2 CPU/node,1 CPU/node}
      \end{axis}
    \end{tikzpicture}
    \label{sfig:results2:perf}
  }

  \subtable[Execution Time Breakdown]{
    \scalebox{0.8}{
   \tiny
    \begin{tabular}{c@{\hspace{2pt}}cD{.}{.}{3}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}}
\toprule
GPUs/ & \# \\
node & nodes & \multicolumn{1}{c}{Wall Clock} & \multicolumn{1}{c}{Application} & \multicolumn{1}{c}{Copies} & \multicolumn{1}{c}{High-level} & \multicolumn{1}{c}{Low-level} & \multicolumn{1}{c}{Mapper} & \multicolumn{1}{c}{System} \\
\midrule
\multirow{4}{*}{$1$} & $1$ & 40.718 & 38.486 & 0.008 & 0.996 & 0.544 & 0 & 0\\
 & $2$ & 25.365 & 43.602 & 0.455 & 2.027 & 0.682 & 0 & 0.043\\
 & $3$ & 21.808 & 49.256 & 0.513 & 2.377 & 0.765 & 0 & 0.06\\
 & $4$ & 17.476 & 53.181 & 0.501 & 2.912 & 0.743 & 0 & 0.072\\
\midrule
\multirow{4}{*}{$2$} & $1$ & 22.289 & 38.55 & 0.009 & 1.694 & 0.68 & 0 & 0\\
 & $2$ & 16.787 & 51.081 & 0.573 & 2.373 & 0.756 & 0 & 0.056\\
 & $3$ & 11.706 & 49.502 & 0.733 & 2.661 & 0.749 & 0 & 0.072\\
 & $4$ & 9.817 & 50.798 & 0.86 & 2.755 & 0.735 & 0 & 0.1\\
\midrule
\multirow{4}{*}{$3$} & $1$ & 15.799 & 38.507 & 0.01 & 2.056 & 0.765 & 0 & 0\\
 & $2$ & 11.462 & 48.698 & 0.951 & 2.682 & 0.819 & 0 & 0.109\\
 & $3$ & 9.363 & 50.786 & 1.282 & 2.976 & 0.767 & 0 & 0.081\\
 & $4$ & 7.26 & 51.778 & 1.285 & 3.172 & 0.818 & 0 & 0.117\\
\midrule
\multirow{4}{*}{$4$} & $1$ & 12.11 & 39.296 & 0.011 & 2.17 & 0.827 & 0 & 0\\
 & $2$ & 10.05 & 49.799 & 1.145 & 3.023 & 0.82 & 0 & 0.24\\
 & $3$ & 6.951 & 51.216 & 1.367 & 3.137 & 0.798 & 0 & 0.12\\
 & $4$ & 6.093 & 52.183 & 1.216 & 3.317 & 0.782 & 0 & 0.135\\
\midrule
\multirow{4}{*}{$6$} & $1$ & 9.031 & 40.265 & 0.013 & 2.536 & 0.969 & 0 & 0\\
 & $2$ & 6.79 & 48.992 & 0.946 & 3.182 & 0.937 & 0 & 0.145\\
 & $3$ & 6.199 & 51.904 & 1.061 & 3.752 & 0.909 & 0 & 0.185\\
 & $4$ & 4.612 & 52.603 & 1.238 & 3.712 & 0.872 & 0 & 0.222\\
\midrule
\multirow{4}{*}{$12$} & $1$ & 7.704 & 45.959 & 0.03 & 4.01 & 1.765 & 0 & 0\\
 & $2$ & 5.547 & 65.432 & 1.019 & 4.762 & 1.328 & 0 & 0.232\\
 & $3$ & 5.577 & 68.74 & 1.059 & 5.922 & 1.384 & 0 & 0.322\\
 & $4$ & 4.017 & 67.662 & 1.19 & 4.882 & 1.22 & 0 & 1.485\\
\bottomrule \\
    \end{tabular}
}
    \label{sfig:results2:timers}
  }

@@
